Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2019-12-06 doc/Paper/main.tex
Started addressing comments from Rachel.

\abstract{We analyze the clustering of galaxies in the first public data release of the Hyper Suprime-Cam Subaru Strategic Program. Despite the relatively small footprints of the observed fields, the data are an excellent proxy for the very deep photometric datasets as will be acquired by the Large Synoptic Survey Telescope, and are therefore an ideal test bed for the analysis methods being implemented by the Dark Energy Science Collaboration. We select a magnitude limited sample with $i<24.5$ and analyze it in four tomographic redshift bins covering the range $0.15\lesssim z\lesssim1.5$. We carry out a Fourier-space analysis of the two-point clustering of this sample, including all auto- and cross-correlations between bins. We demonstrate the use of map-level deprojection methods to account for non-physical fluctuations in the galaxy number density caused by observational systematics. Through a halo occupation distribution analysis, we place constraints on the characteristic halo masses of this sample as a function of redshift, finding a good fit up to scales $k_{\rm max}=1\,{\rm Mpc}^{-1}$, including both auto- and cross-correlations. Our results show monotonically decreasing average halo masses with increasing redshift, which can be interpreted in terms of the drop-out of red galaxies at high redshifts for a flux-limited sample, consistent with previous analyses. In terms of photometric redshift systematics, we show that additional care is needed in order to marginalize over uncertainties in the redshift distribution in galaxy clustering, even for samples of this small size, and that these uncertainties can be significantly constrained by including cross-bin correlations. We are able to make a $\sim3\sigma$ detection of the effects of lensing magnification in the HSC data. Our results are stable to variations in the amplitude of density fluctuations $\sigma_8$ and the cold dark matter abundance $\Omega_c$ and we find constraints that agree well with measurements from Planck and low-redshift probes. Finally, we use our analysis pipeline to study the clustering of galaxies as a function of limiting flux, and provide a simple fitting function for the linear galaxy bias for magnitude limited samples as a function of limiting magnitude and redshift.}

@@

\section{Introduction}\label{sec:intro}
  The past two decades have seen a revolution in our understanding of the Universe and its constituents. While observations of the cosmic microwave background (CMB) play a pivotal role in anchoring the standard  cosmological model \cite{Planck:2018}, they are not a direct probe of the physics of the low redshift Universe. In order to directly characterize properties of dark energy and modified gravity, we need to measure the expansion history and growth  \cite{1903.12016}. At the moment, this is only possible with optical large scale structure surveys.

  Over a decade ago, the Dark Energy Task Force divided the evolution of optical experiments into approximate stages \cite{0609591}. The current Stage III experiments, including spectroscopic surveys such as eBOSS \cite{1707.09322,Zhu:2018,1712.08064,1801.02689,1801.02891} and VIPERS \cite{1611.07048,1612.05645,1708.00026} and photometric surveys such as DES \cite{1708.01531,1708.01530,1708.01536}, the Hyper Suprime-Cam \cite{1704.05858,2019PASJ...71...43H,1906.06041} and the Kilo-Degree Survey / VIKING-450 \cite{1902.11265,1812.06077,Joudaki:2019} are approaching completion and the field is preparing for the Stage IV surveys, such as the ground-based DESI \cite{1611.00036,1907.10688} and LSST \cite{0912.0201,1809.01669}, as well as major satellite missions like Euclid \cite{1606.00180} and WFIRST \cite{1904.01174}.

  Together with transformational sensitivity increases in the Stage IV surveys, the challenges of understanding and controlling systematic errors are becoming considerably more difficult \cite{1808.07335}. For photometric surveys, the deep surveys sensitive to many more sources inevitably come with crowded fields where blending affects a significant fraction of all sources. The increased blending leads to new uncertainties in isolating sources, measuring their fluxes (required for photometric redshifts) and inferring their shear estimates. These effects in turn lead to subtle sample selection effects, which are amplified by the interaction of the point spread function (PSF) with blending \cite{1708.01533,1905.01324,1907.10572}. But even with perfect measurements of fluxes, our ability to infer source redshift distributions is hampered by incompleteness in spectroscopic samples used to calibrate redshifts \cite{1903.09325}. Finally, at the depths of Stage IV photometric surveys, instrumental and observational effects, such as scattered light from bright objects, errors in star-galaxy separation, reddening by Milky Way dust, and varying observing conditions, will imprint spurious fluctuations on the observed galaxy density field. These fluctuations will, if not correctly accounted for, masquerade as intrinsic large-scale fluctuations in the cosmic density field. Therefore, Stage IV photometric experiments are likely to be limited by our ability to control systematics rather than the intrinsic statistical power of the survey.

  The community is well aware of these challenges lying ahead. There are two main approaches to preparing for the arrival of data. On one hand, we are building sophisticated, realistic mock data sets, such as LSST Dark Energy Science Collaboration (DESC) Data Challenge 2 \cite{1909.07340,1907.06530}. On the other hand, we are (re-)analyzing existing precursor data to test-drive our methods and codes in a realistic environment. In this paper, we focus on the latter approach and perform an analysis of photometric galaxy clustering using the first data release (DR1) of the Hyper Suprime-Cam Subaru Strategic Program (HSC-SSP) \cite{2018PASJ...70S...8A}. This dataset bears significant similarities to the data expected from LSST, both in terms of survey depth and photometric bands as well as primary data reduction and catalog generation. Specifically, HSC covers essentially the same bands as LSST, with the exception of missing the UV $u$-band fluxes. In this work, we focus on a magnitude-limited galaxy sample with limiting magnitude $i<24.5$, which is similar to the expected 5-$\sigma$ detection limit for LSST after one year \cite{1809.01669} ($i<25.1$). Finally, the primary data reduction codes used in HSC-SSP and planned for LSST are of the same lineage, employing much of the same methods \cite{2018PASJ...70S...5B,1812.03248}. With the exception of a rather small sky area of around 90 square degrees used in this paper, the HSC-SSP data is therefore a perfect proxy for future LSST data. This analysis has the additional attraction that no other photometric galaxy clustering study has been carried out with these data.

  In this work, we present an analysis of photometric galaxy clustering using HSC DR1 data\footnote{We note that we do not blind our results in any stage of the analysis.}. We split the data into four tomographic redshift bins and measure both the auto- and cross-power spectra of all bins, correcting for observational systematics using mode deprojection. We then use the halo model coupled with a halo occupation distribution to fit the data and derive constraints on astrophysical parameters, marginalizing over photometric redshift uncertainties. To ensure the stability of our results, we perform a suite of complementary analyses and find our constraints to be robust to photometric redshift uncertainties. We additionally perform extended analyses in which we compute constraints on lensing magnification in our sample and allow for variations in the $\Lambda$CDM cosmological parameters, respectively. Finally, we use our data to derive a simple fitting function for the linear galaxy bias as a function of redshift and limiting magnitude of the sample.

  In our analysis, we make several simplifying approximations; in particular we employ a simple semi-analytical halo model to derive theoretical predictions for the data, which will most certainly not be sophisticated enough for the full sky LSST analysis. The analysis of LSST data will likely require  a combination of  bias expansion approaches \cite{0902.0991,1402.5916,1611.09787,1910.07097} and power spectrum emulators \cite{1804.05865,1705.03388}. However, given the level of statistical precision of the data at hand, we find that a simple halo model suffices, and thus use it as a ``good enough'' substitute for the final modeling.

@@

  \begin{table}
  \centering
  \begin{tabular}{|l|r|c|l|}
   \hline
   {\bf Field name} & $N_{\rm gal}$ & {\bf Area} (deg$^2$) & $f_{\rm sky}$ \\
   \hline
   GAMA09H  & 1,697,713 & 14.5 & $3.5\times10^{-4}$ \\
   GAMA15H  & 1,695,364 & 15.1 & $3.7\times10^{-4}$ \\
   HECTOMAP &   639,970 &  5.1 & $1.2\times10^{-4}$ \\
   VVDS     & 2,340,965 & 20.6 & $5.0\times10^{-4}$ \\
   WIDE12H  & 1,220,816 & 11.6 & $2.8\times10^{-4}$ \\
   XMMLSS   & 2,139,629 & 20.8 & $5.0\times10^{-4}$ \\
   \hline
   Total    & 9,734,457 & 87.7 & $2.1\times10^{-3}$ \\
   \hline
  \end{tabular}
  \caption{Summary of the 6 different fields used in our analysis. The second column lists the number of galaxies in the DR1 catalog passing the cuts in Table \ref{tab:cuts_summary}. The third and fourth columns show the area and corresponding sky fraction covered by each field. The area was calculated as the sum of pixel areas allowed by the sky mask described in Section \ref{ssec:methods.mask}. We note that the HECTOMAP field is not included in our analysis due to its smaller area.} \label{tab:field_summary}
  \end{table}

@@

  HSC-SSP is a photometric galaxy survey that has been awarded 300 nights on the Subaru Telescope starting in 2014. DR1 includes data from 61.5 nights observed to three different depths: Wide (108 square degrees to $i\sim 26.4$), Deep (26 square degrees to $i\sim26.5$) and UltraDeep (4 square degrees to $i\sim 27$). In this work we focus on the HSC Wide field, which has been observed in five broadband filters ($grizy$) and is distributed among 6 fields  of areas varying between 5 and 20 square degrees. The image quality is impressive with a median seeing of around 0.6 arcsec, which is considerably better than other comparable surveys (e.g. DES with around 0.9 arcsec) and also likely better than the median seeing expected to be achieved by LSST. The data are processed with \texttt{hscPipe} \cite{2018PASJ...70S...5B} and are available to the community through a public database.

@@

  \subsection{Survey mask}\label{ssec:methods.mask}
    \begin{figure}
      \centering
      \includegraphics[width=0.49\textwidth]{figures/mask_GAMA09H.pdf}
      \includegraphics[width=0.49\textwidth]{figures/mask_GAMA15H.pdf}
      \includegraphics[width=0.49\textwidth]{figures/mask_HECTOMAP.pdf}
      \includegraphics[width=0.49\textwidth]{figures/mask_VVDS.pdf}
      \includegraphics[width=0.49\textwidth]{figures/mask_WIDE12H.pdf}
      \includegraphics[width=0.49\textwidth]{figures/mask_XMMLSS.pdf}
      \caption{Sky masks for the 6 fields used in this analysis. The map pixels contain values between 0 and 1, corresponding to the fraction of the pixel's area not covered by the fiducial bright-object mask.}
      \label{fig:masks}
    \end{figure}
    The reconstruction of the survey geometry is a central step in order to obtain unbiased estimates of the angular power spectrum. This information is encoded in the so-called ``survey mask'', which minimally contains binary information about which areas of the sky should (mask $=1$) or should not (mask $=0$) be used in the analysis. The basis for our survey mask is the so-called ``bright-object mask'' \cite{2018PASJ...70S...7C}, provided with the HSC DR1, which flags sources that are close to bright stars (mag $<17.5$), with a magnitude-dependent exclusion radius (see \cite{2018PASJ...70S...7C} for details). The information about the bright object mask is encoded in the HSC DR1 at the catalog level in terms of per-object flags. We transform this information into a pixelized sky map through a multi-step process:
    \begin{enumerate}
      \item We start by creating a low-resolution binary mask based on the presence of objects from the raw catalog in a given pixel. This mask has a pixel size of 0.6 arcmin. The large number density of the raw catalog  ($n_g\sim30\,{\rm arcmin}^{-2}$) is high enough that masked pixels are unlikely to correspond to intrinsically empty regions of the sky, but rather completely unobserved pixels.
      \item We upgrade the low-resolution binary mask to a higher resolution ($0.2$ arcmin), and remove all pixels containing objects flagged by the bright object mask. We then remove all disconnected, unmasked groups of pixels, corresponding to spurious islands within the exclusion radius of a bright object with no sources in the catalogs.
      \item We downgrade the resulting mask back to the original resolution through an averaging procedure, producing a map quantifying the observed fraction of each pixel.
    \end{enumerate}
    We verified that the resulting mask is robust by comparing the obtained power spectra to those found with an observed fraction map defined simply as the fraction of objects in each pixel outside the bright object mask. The resolution of our fiducial mask ($0.6$ arcminutes) defines the resolution of all maps used in this analysis. After this procedure, we further mask all pixels with a $10\sigma$ depth below our magnitude limit of $i<24.5$, where the depth is estimated as described in Section \ref{ssec:methods.syst}.

@@

      \caption{Maps of different observational systematics that could cause an artificial modulation in the inferred galaxy overdensity. The maps correspond to the XMMLSS field, and were obtained as described in Section \ref{ssec:methods.syst}. From top to bottom and left to right, the different panels show maps of the seeing in the $g$, $i$ and $y$ bands, airmass in the $y$ band, sky level in the $i$ band, $10\sigma$ $i$-band depth, dust absorption and star density. We can visually appreciate the existing correlations between different systematics (e.g. seeing and airmass), which are automatically taken into account by the deprojection method described in Section \ref{ssec:methods.cell} and in \cite{2019MNRAS.484.4127A}.}

@@

    A number of astrophysical and observational systematic effects can affect the observed distribution of galaxies, and therefore may bias our inference of their clustering properties. To mitigate this effect, we deproject maps of these systematics from our data, as described in Section \ref{ssec:methods.cell}. We generate maps of the most plausible sources of systematic variations in the galaxy number density:

@@

    To estimate the fiducial redshift distributions used in our main analysis, we make use of the COSMOS 30-band photometric catalog of \cite{2016ApJS..224...24L}. The idea is to use the high-fidelity photo-$z$ estimates in the COSMOS 30-band data as the truth, in which case one can estimate the redshift distribution by simply histograming these redshifts with appropriate weights. These weights are calculated following the procedure described in \cite{2017MNRAS.465.1454H,2019PASJ...71...43H}, which we summarize here for completeness:
    \begin{enumerate}
      \item We first cross-match all objects in the COSMOS 30-band catalog with sources in the HSC COSMOS field that satisfy our sample selection cuts (see Section \ref{sec:data}). Matches are found as pairs of objects with an angular separation smaller than 1 arcsecond. All unmatched objects in either catalog are discarded.
      \item For each object in the COSMOS 30-band data with a match in HSC, we find its $N_{\rm neigh}^{\rm COSMOS}=20$ nearest neighbors in the COSMOS 30-band sample within the 5-dimensional space of HSC apparent magnitudes $(g,r,i,z,y)$ using a Euclidean metric. We record the distance to the furthest neighbor in this space.
      \item We then compute the number of HSC sources $N_{\rm neigh}^{\rm HSC}$ found within the same radius in magnitude space. The weight applied to the COSMOS 30-band object is then given by the ratio $N^{\rm HSC}_{\rm neigh}/N^{\rm COSMOS}_{\rm neigh}$ normalized by the total number of objects in each sample.
    \end{enumerate}
    There are a number of caveats associated with this method to estimate redshift distributions. First, the COSMOS 30-band photometric redshifts have a lower redshift accuracy and precision than a purely spectroscopic sample. Second, the small area covered by COSMOS may lead to sample variance uncertainties in the inferred redshift distributions that are difficult to quantify, particularly if the color-redshift relation has an environmental dependence. Finally, the photo-$z$ codes used in HSC DR1 were trained on the COSMOS 30-band data, which could lead to circularity in the estimation of the redshift distributions.

@@

    Given the small size of the sky patches covered by HSC DR1, we will adopt the flat sky approximation for simplicity, in which case $\nv$ is a 2D vector. It is common to decompose $\delta^i_g(\nv)$ into its Fourier coefficients
    \begin{equation}
      a^i_{\bf l}\equiv \int\frac{\mathrm{d}\theta^2}{2\pi}e^{-i{\bf l}\cdot\nv}\delta^i_g(\nv).
    \end{equation}
    The variance of the Fourier coefficients is the so-called angular power spectrum $\langle a^i_{\bf l}a^{j*}_{{\bf l}'}\rangle = C^{ij}_\ell\,\delta^{\cal D}({\bf l}-{\bf l}')$, where $\delta^{\cal D}$ is the 2D Dirac delta function. The 3D power spectrum $P_{gg}(z,{\bf k})$ is defined analogously for the 3D Fourier coefficients of $\Delta_g$. Both quantities are related to each other through:
    \begin{equation}\label{eq:cell_gg_limber}
      C^{ij}_\ell = \int \mathrm{d}z\,\frac{H(z)}{\chi^2(z)} p^i(z)p^j(z)\,P_{gg}\left(z,k=\frac{\ell+1/2}{\chi(z)}\right),
    \end{equation}
    where $H(z)$ is the expansion rate at redshift $z$, and we have used the so-called Limber approximation\footnote{We note that we have compared the power spectra for the redshift distributions employed in this work obtained with the Limber approximation and those obtained making no approximations. We find the results to be virtually the same and in the following we therefore use the Limber approximation to compute projected power spectra for computational speed.} \citep{Limber:1953, Kaiser:1992, Kaiser:1998}. In this work, we compute theoretical predictions for angular power spectra using \texttt{CCL}\footnote{\url{https://github.com/LSSTDESC/CCL}.} \cite{Chisari:2019}.

>>>>

\abstract{We analyze the clustering of galaxies in the first public data release of the Hyper Suprime-Cam Subaru Strategic Program. Despite the relatively small footprints of the observed fields, the data are an excellent proxy for the very deep photometric datasets that will be acquired by the Large Synoptic Survey Telescope, and are therefore an ideal test bed for the analysis methods being implemented by the LSST Dark Energy Science Collaboration. We select a magnitude limited sample with $i<24.5$ and analyze it in four tomographic redshift bins covering the range $0.15\lesssim z\lesssim1.5$. We carry out a Fourier-space analysis of the two-point clustering of this sample, including all auto- and cross-correlations between bins. We demonstrate the use of map-level deprojection methods to account for non-physical fluctuations in the galaxy number density caused by observational systematics. Through a halo occupation distribution analysis, we place constraints on the characteristic halo masses of this sample as a function of redshift, finding a good fit up to scales $k_{\rm max}=1\,{\rm Mpc}^{-1}$, including both auto- and cross-correlations. Our results show monotonically decreasing average halo masses with increasing redshift, which can be interpreted in terms of the drop-out of red galaxies at high redshifts for a flux-limited sample, consistent with previous analyses. In terms of photometric redshift systematics, we show that additional care is needed in order to marginalize over uncertainties in the redshift distribution in galaxy clustering, even for samples of this small size, and that these uncertainties can be significantly constrained by including cross-bin correlations. We are able to make a $\sim3\sigma$ detection of the effects of lensing magnification in the HSC data. Our results are stable to variations in the amplitude of density fluctuations $\sigma_8$ and the cold dark matter abundance $\Omega_c$ and we find constraints that agree well with measurements from Planck and low-redshift probes. Finally, we use our analysis pipeline to study the clustering of galaxies as a function of limiting flux, and provide a simple fitting function for the linear galaxy bias for magnitude limited samples as a function of limiting magnitude and redshift.}

@@

\section{Introduction}\label{sec:intro}
  The past two decades have seen a revolution in our understanding of the Universe and its constituents. While observations of the cosmic microwave background (CMB) play a pivotal role in anchoring the standard  cosmological model \cite{Planck:2018}, they are not a direct probe of the physics of the low-redshift Universe. In order to directly characterize properties of dark energy and modified gravity, we need to measure the expansion history and growth  \cite{1903.12016}. At the moment, this is only possible with optical large scale structure surveys.

  Over a decade ago, the Dark Energy Task Force divided the evolution of optical experiments into approximate stages \cite{0609591}. The current Stage III experiments, including spectroscopic surveys such as eBOSS \cite{1707.09322,Zhu:2018,1712.08064,1801.02689,1801.02891} and VIPERS \cite{1611.07048,1612.05645,1708.00026} and photometric surveys such as DES \cite{1708.01531,1708.01530,1708.01536}, the Hyper Suprime-Cam survey \cite{1704.05858,2019PASJ...71...43H,1906.06041} and the Kilo-Degree Survey / VIKING-450 \cite{1902.11265,1812.06077,Joudaki:2019} are approaching completion and the field is preparing for the Stage IV surveys, such as the ground-based DESI \cite{1611.00036,1907.10688} and LSST \cite{0912.0201,1809.01669, Ivezic:2019}, as well as major satellite missions like Euclid \cite{1606.00180} and WFIRST \cite{1904.01174}.

  Together with transformational sensitivity increases in the Stage IV surveys, the challenges of understanding and controlling systematic errors are becoming considerably more difficult \cite{1808.07335}. For photometric surveys, the deep surveys sensitive to many more sources inevitably come with crowded fields where blending affects a significant fraction of all sources. The increased blending leads to new uncertainties in isolating sources, measuring their fluxes (required for photometric redshifts) and inferring their weak gravitational lensing shear estimates. These effects in turn lead to subtle sample selection effects, which are amplified by the interaction of the point spread function (PSF) with blending \cite{1708.01533,1905.01324,1907.10572}. But even with perfect measurements of fluxes, our ability to infer source redshift distributions is hampered by incompleteness in spectroscopic samples used to train and calibrate redshifts \cite{1903.09325}. Finally, at the depths of Stage IV photometric surveys, instrumental and observational effects, such as scattered light from bright objects, errors in star-galaxy separation, reddening by Milky Way dust, and varying observing conditions, will imprint spurious fluctuations on the observed galaxy density field. These fluctuations will, if not correctly accounted for, masquerade as intrinsic large-scale fluctuations in the cosmic density field. Therefore, Stage IV photometric experiments are likely to be limited by our ability to control systematics rather than the intrinsic statistical power of the survey.

  The community is well aware of these challenges lying ahead. There are two main approaches to preparing for the arrival of data. On one hand, we are building sophisticated, realistic mock data sets, such as LSST Dark Energy Science Collaboration (DESC) Data Challenge 2 \cite{1909.07340,1907.06530}. On the other hand, we are (re-)analyzing existing precursor data to validate our methods and codes in a realistic environment. In this paper, we focus on the latter approach and perform an analysis of photometric galaxy clustering using the first data release (DR1) of the Hyper Suprime-Cam Subaru Strategic Program (HSC-SSP) \cite{2018PASJ...70S...8A}. This dataset bears significant similarities to the data expected from LSST, both in terms of survey depth and photometric bands as well as primary data reduction and catalog generation. Specifically, HSC covers essentially the same bands as LSST, with the exception of missing the UV $u$-band fluxes. In this work, we focus on a magnitude-limited galaxy sample with limiting magnitude $i<24.5$, which is similar to the expected 5-$\sigma$ detection limit for LSST after one year \cite{1809.01669} ($i<25.1$). Finally, the primary data reduction codes used in HSC-SSP and planned for LSST are of the same lineage, employing many of the same methods \cite{2018PASJ...70S...5B,1812.03248}. With the exception of a rather small sky area of around 90 square degrees used in this paper, the HSC-SSP data is therefore a perfect proxy for future LSST data. This analysis has the additional attraction that no other photometric galaxy clustering study has been carried out with these data.

  In this work, we present an analysis of photometric galaxy clustering using HSC DR1 data\footnote{We note that we do not blind our results in any stage of the analysis.}. We split the data into four tomographic redshift bins and measure both the auto- and cross-power spectra of all bins, correcting for observational systematics using mode deprojection. We then use the halo model coupled with a halo occupation distribution to fit the data and derive constraints on astrophysical parameters, marginalizing over photometric redshift (photo-$z$) uncertainties. To ensure the stability of our results, we perform a suite of complementary analyses and find our constraints to be robust to photometric redshift uncertainties. We additionally perform extended analyses in which we compute constraints on lensing magnification in our sample and allow for variations in the $\Lambda$CDM cosmological parameters, respectively. Finally, we use our data to derive a simple fitting function for the linear galaxy bias as a function of redshift and limiting magnitude of the sample.

  In our analysis, we make several simplifying approximations; in particular we employ a simple semi-analytical halo model to derive theoretical predictions for the data, which will most certainly not be sophisticated enough for the full sky LSST analysis. The analysis of LSST data will likely require  a combination of  bias expansion approaches \cite{0902.0991,1402.5916,1611.09787,1910.07097} and power spectrum emulators \cite{1804.05865,1705.03388}. However, we find that a simple halo model suffices to describe the data at the current level of precision.

@@

  \begin{table}
  \centering
  \begin{tabular}{|l|r|c|l|}
   \hline
   {\bf Field name} & $N_{\rm gal}$ & {\bf Area} (deg$^2$) & $f_{\rm sky}$ \\
   \hline
   GAMA09H  & 1,697,713 & 14.5 & $3.5\times10^{-4}$ \\
   GAMA15H  & 1,695,364 & 15.1 & $3.7\times10^{-4}$ \\
   HECTOMAP &   639,970 &  5.1 & $1.2\times10^{-4}$ \\
   VVDS     & 2,340,965 & 20.6 & $5.0\times10^{-4}$ \\
   WIDE12H  & 1,220,816 & 11.6 & $2.8\times10^{-4}$ \\
   XMM-LSS   & 2,139,629 & 20.8 & $5.0\times10^{-4}$ \\
   \hline
   Total    & 9,734,457 & 87.7 & $2.1\times10^{-3}$ \\
   \hline
  \end{tabular}
  \caption{Summary of the 6 different fields used in our analysis. The second column lists the number of galaxies in the DR1 catalog passing the cuts in Table \ref{tab:cuts_summary}. The third and fourth columns show the area and corresponding sky fraction covered by each field. The area was calculated as the sum of pixel areas allowed by the sky mask described in Section \ref{ssec:methods.mask}. We note that the HECTOMAP field is not included in our analysis due to its smaller area.} \label{tab:field_summary}
  \end{table}

@@

  HSC-SSP is a photometric galaxy survey that has been awarded 300 nights on the Subaru Telescope starting in 2014. DR1 includes data from 61.5 nights observed to three different depths: Wide (108 square degrees to $i\sim 26.4$), Deep (26 square degrees to $i\sim26.5$) and UltraDeep (4 square degrees to $i\sim 27$). In this work we focus on the HSC Wide field, which has been observed in five broadband filters ($grizy$) and is distributed among 6 fields  of areas varying between 5 and 20 square degrees. The image quality is impressive with a median $i$-band seeing of around 0.6 arcsec, which is considerably better than other comparable surveys (e.g. DES with around 0.9 arcsec in the $riz$-bands) and also likely better than the median seeing expected to be achieved by LSST. The data are processed with \texttt{hscPipe} \cite{2018PASJ...70S...5B} and are available to the community through a public database.

@@

  \subsection{Survey mask}\label{ssec:methods.mask}
    \begin{figure}
      \centering
      \includegraphics[width=0.49\textwidth]{figures/mask_GAMA09H.pdf}
      \includegraphics[width=0.49\textwidth]{figures/mask_GAMA15H.pdf}
      \includegraphics[width=0.49\textwidth]{figures/mask_HECTOMAP.pdf}
      \includegraphics[width=0.49\textwidth]{figures/mask_VVDS.pdf}
      \includegraphics[width=0.49\textwidth]{figures/mask_WIDE12H.pdf}
      \includegraphics[width=0.49\textwidth]{figures/mask_XMMLSS.pdf}
      \caption{Sky masks for the 6 fields used in this analysis. The map pixels contain values between 0 and 1, corresponding to the fraction of the pixel's area not covered by the fiducial bright-object mask.}
      \label{fig:masks}
    \end{figure}
    The reconstruction of the survey geometry is a central step in order to obtain unbiased estimates of the angular power spectrum. This information is encoded in the so-called ``survey mask'', which minimally contains binary information about which areas of the sky should (mask $=1$) or should not (mask $=0$) be used in the analysis. The basis for our survey mask is the so-called ``bright-object mask'' \cite{2018PASJ...70S..25M}, provided with the HSC DR1, which flags sources that are close to bright stars (mag $<17.5$), with a magnitude-dependent exclusion radius (the so-called ``Sirius'' mask, see \cite{2018PASJ...70S..25M} for details). The information about the bright object mask is encoded in the HSC DR1 at the catalog level in terms of per-object flags. We transform this information into a pixelized sky map through a multi-step process:
    \begin{enumerate}
      \item We start by creating a low-resolution binary mask based on the presence of objects from the raw catalog in a given pixel. This mask has a pixel size of 0.6 arcmin. The large number density of the raw catalog  ($n_g\sim30\,{\rm arcmin}^{-2}$) is high enough that masked pixels are unlikely to correspond to intrinsically empty regions of the sky, but rather completely unobserved pixels.
      \item We upgrade the low-resolution binary mask to a higher resolution ($0.2$ arcmin), and remove all pixels containing objects flagged by the bright object mask. We then remove all disconnected, unmasked groups of pixels, corresponding to spurious islands within the exclusion radius of a bright object with no sources in the catalogs.
      \item We downgrade the resulting mask back to the original resolution through an averaging procedure, producing a map quantifying the observed fraction of each pixel.
    \end{enumerate}
    We verified that the resulting mask is robust by comparing the obtained power spectra to those found with an observed fraction map defined simply as the fraction of objects in each pixel outside the bright object mask. The resolution of our fiducial mask ($0.6$ arcminutes) defines the resolution of all maps used in this analysis. After this procedure, we further mask all pixels with a $10\sigma$ depth below our magnitude limit of $i<24.5$, where the depth is estimated as described in Section \ref{ssec:methods.syst}.

@@

      \caption{Maps of different observational systematics that could cause an artificial modulation in the inferred galaxy overdensity. The maps correspond to the XMM-LSS field, and were obtained as described in Section \ref{ssec:methods.syst}. From left to right and top to bottom, the different panels show maps of the seeing in the $g$, $i$ and $y$ bands, airmass in the $y$ band, sky level in the $i$ band, $10\sigma$ $i$-band depth, dust absorption and star density. We can visually appreciate the existing correlations between different systematics (e.g. seeing and airmass), which are automatically taken into account by the deprojection method described in Section \ref{ssec:methods.cell} and in \cite{2019MNRAS.484.4127A}.}

@@

    A number of astrophysical and observational systematic effects can modify the observed distribution of galaxies, and therefore may bias our inference of their clustering properties. To mitigate this effect, we deproject maps of these systematics from our data, as described in Section \ref{ssec:methods.cell}. We generate maps of the most plausible sources of systematic variations in the galaxy number density:

@@

    To estimate the fiducial redshift distributions used in our main analysis, we make use of the COSMOS 30-band photometric catalog of \cite{2016ApJS..224...24L}. The idea is to use the high-fidelity photo-$z$ estimates in the COSMOS 30-band data as the truth, in which case one can estimate the redshift distribution by simply making a histogram these redshifts with appropriate weights. These weights are calculated following the procedure described in \cite{2017MNRAS.465.1454H,2019PASJ...71...43H}, which we summarize here for completeness:
    \begin{enumerate}
      \item We first cross-match all objects in the COSMOS 30-band catalog with sources in the HSC COSMOS field that satisfy our sample selection cuts (see Section \ref{sec:data}). Matches are found as pairs of objects with an angular separation smaller than 1 arcsecond. All unmatched objects in either catalog are discarded.
      \item For each object in the COSMOS 30-band data with a match in HSC, we find its $N_{\rm neigh}^{\rm COSMOS}=20$ nearest neighbors in the COSMOS 30-band sample within the 5-dimensional space of HSC apparent magnitudes $(g,r,i,z,y)$ using a Euclidean metric. We record the distance to the furthest neighbor in this space.
      \item We then compute the number of HSC sources $N_{\rm neigh}^{\rm HSC}$ found within the same radius in magnitude space. The weight applied to the COSMOS 30-band object is then given by the ratio $N^{\rm HSC}_{\rm neigh}/N^{\rm COSMOS}_{\rm neigh}$ normalized by the total number of objects in each sample.
    \end{enumerate}
    There are a number of caveats associated with this method to estimate redshift distributions. First, the COSMOS 30-band photometric redshifts have a lower redshift accuracy and precision than a purely spectroscopic sample. Second, the small area covered by COSMOS may lead to sample variance uncertainties in the inferred redshift distributions that are difficult to quantify, particularly if the color-redshift relation has an environmental dependence. Finally, the photo-$z$ codes used in HSC DR1 were trained on the COSMOS 30-band data, which could lead to circularity in the estimation of the redshift distributions.

@@

    Given the small size of the sky patches covered by HSC DR1, we will adopt the flat sky approximation for simplicity, in which case $\nv$ is a 2D vector. It is common to decompose $\delta^i_g(\nv)$ into its Fourier coefficients
    \begin{equation}
      a^i_{\bf l}\equiv \int\frac{\mathrm{d}\theta^2}{2\pi}e^{-i{\bf l}\cdot\nv}\delta^i_g(\nv).
    \end{equation}
    The variance of the Fourier coefficients is the so-called angular power spectrum $\langle a^i_{\bf l}a^{j*}_{{\bf l}'}\rangle = C^{ij}_\ell\,\delta^{\cal D}({\bf l}-{\bf l}')$, where $\delta^{\cal D}$ is the 2D Dirac delta function. The 3D power spectrum $P_{gg}(z,{\bf k})$ is defined analogously for the 3D Fourier coefficients of $\Delta_g$. Both quantities are related to each other through:
    \begin{equation}\label{eq:cell_gg_limber}
      C^{ij}_\ell = \int \mathrm{d}z\,\frac{H(z)}{\chi^2(z)} p^i(z)p^j(z)\,P_{gg}\left(z,k=\frac{\ell+1/2}{\chi(z)}\right),
    \end{equation}
    where $H(z)$ is the expansion rate at redshift $z$, and we have used the so-called Limber approximation\footnote{We note that we have compared the power spectra for the redshift distributions employed in this work obtained with the Limber approximation and those obtained making no approximations. We find the results to be virtually the same and in the following we therefore use the Limber approximation to compute projected power spectra for computational speed.} \citep{Limber:1953, Kaiser:1992, Kaiser:1998}. In this work, we compute theoretical predictions for angular power spectra using the DESC Core Cosmology Library (\texttt{CCL}\footnote{\url{https://github.com/LSSTDESC/CCL}.}) \cite{Chisari:2019}.
